Møil: A web-based administration tool for mail servers backed by relational databases

### 2014-07-28 doc/study/study.tex
Little changes to Møil data model and modoboa sections.

@@

			\subsubsection*{Relocations}
				The relocation model is in fact updated but actually not
				further used, currently. Whenever a \texttt{Domain} or
				\texttt{Mailbox} is renamed, it is necessary to move the
				corresponding folders in the file system of the Mail Store.
				These moves are represented as \texttt{Relocation} resources,
				which can be read by a daemon (yet to be implemented) running
				on the actual Mail Store.
				\todo{Other solutions?}

>>>>

				\emph{modoboa} seems the most mature of the compared tools. It
				uses the Python Django framework and therefore includes
				facilities like schema migrations.

@@

			\subsubsection*{Relocations}
				The relocation model is in fact updated but actually not
				further used, currently. Whenever a \texttt{Domain} or
				\texttt{Mailbox} is renamed, it is necessary to move the
				corresponding folders in the file system of the Mail Store.
				These moves are represented as \texttt{Relocation} resources
				saving \texttt{old\_domain} and \texttt{old\_username} values,
				which can be read by a daemon (yet to be implemented) running
				on the actual Mail Store.

				\todo{Other solutions?}
